---
title: "INFO 550 Report"
author: "Cheng Lyu"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    highlights: "pygments"
---

```{r, option, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE
)
```

## Set up parameters 
We first set the parameters we used to simulate a dataset with two biomarkers from a logistic regression.

```{r, setup}
set.seed(1234)
p <- 1 # known biomarkers
q <- 1 # new biomarkers
beta <- c(1, 2, 0) # testing for the null hypothesis
n <- 1000
```

## Simulate the dataset
```{r, simulation}
# sample from multi-normal distribution
biomarker <- MASS::mvrnorm(n, rep(0, p + q), diag(1, p + q))
z <- cbind(1, biomarker) %*% beta
prob <- as.numeric(1 / (1 + exp(-z)))
Y <- rbinom(n, 1, prob)
n_1 <- sum(Y == 1)
n_0 <- sum(Y == 0)

# construct dataset
mydata <- data.frame(Y = Y, X = biomarker, label = factor(Y, label = c("Controls", "Cases")))
mydata <- mydata[order(mydata$Y, decreasing = T), ]
rownames(mydata) <- NULL
colnames(mydata)[2:3] <- c("First Biomarker", "Second Biomarker")
case <- as.matrix(mydata[mydata$Y == 1, -1])
control <- as.matrix(mydata[mydata$Y == 0, -1])
```
We have `r n_1` cases, and `r n_0` controls. A summary of values for each biomarker in both cases and controls are shown in the table below.

```{r, get-table, echo = FALSE}
knitr::kable(summary(arsenal::tableby(label ~ `First Biomarker` + `Second Biomarker`, mydata)), digits = 2)
```

## Fit logistic regression
```{r, fit-model}
# true underlying standardized coefficients
theta <- beta[3:(p + q + 1)] / beta[2]

# estimate mle of logistic regression
mod <- glm(Y ~ ., family = "binomial", data = mydata)
theta_hat <- mod$coefficients[3:(p + q + 1)] / mod$coefficients[2]
```
As we can see, the true coefficient is `r theta`, and our maximum likelihood estimate is `r round(theta_hat, 4)`. Therefore, thhe underlying true model is the logistic regression.